% cv-en for alexandre medeiros
%   by alemedeiros
%
% my curriculum vitae -- english version
%
% created: 2013-05-26
% last revision: 2013-05-26

\documentclass[10pt,a4paper,sans]{moderncv}
\usepackage{fullpage}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% cv style
\moderncvtheme[black]{classic}

% personal info
\firstname{Alexandre}
\familyname{Medeiros}

% optional info
\title{Curriculum Vitae}
\address{202 Eng. Humberto S. de Camargo Street}{13083-780. Campinas, São Paulo,
Brazil}
\mobile{+55~(11)~96624~2947}
\email{alexandre.medeiros@students.ic.unicamp.br}
\homepage{http://alemedeiros.sdf.org}
\extrainfo{alemedeiros on gitorious, github}

\begin{document}
\makecvtitle
\section{Summary}
{
  I am Interested in many topics of computer science, like theory of
  computation, computer architecture, and algorithms, I am also fond of
  mathematics. I use and support Free Software.
}

\section{Education}
\cventry{2011--}{B.Sc. in Computer Science}{University of Campinas}{Campinas,
São Paulo, Brazil}{}{Ongoing (Expected date of graduation: July 2015).}

\section{Experience}

\subsection{Academic}

\cventry{2013--}{ARM Power Estimations for Mobile Devices}{Undergraduate
Research}{University of Campinas}{Campinas, São Paulo, Brazil}{Advisor: Prof.
Dr. Edson Borin (IC-Unicamp). Co-Advisor: Prof. Dr. Sandro Rigo (IC-Unicamp).
Funded by a Samsung Scholarship}

\cventry{2013}{Teaching Assistant}{Programa de Apoio Didático}{University of
Campinas}{Campinas, São Paulo, Brazil}{
  \begin{itemize}
    \item MC404 -- Basic Organization of Computers and Assembly Language --
      Prof.  Dr. Edson Borin -- 1st semester of 2013.
    \item MC202 -- Data Structures -- Prof.  Dr. Tomasz Kowaltowski -- 2nd
      semester of 2012.
    \item MC202 -- Data Structures -- Prof.  Dr. Cid Carvalho de Souza -- 1st
      semester of 2012.
  \end{itemize}
}

\subsection{Volunteer}

\cventry{2011--}{Administrative Officer}{CACo}{University of Campinas}{Campinas,
São Paulo, Brazil}{Unicamp Computing Students' Union.}

\cventry{2012--}{Undergraduate Representative}{Institute of Computing}
{University of Campinas}{Campinas, São Paulo, Brazil}{Undergraduate
representative in the Undergraduate Affairs Commission of the Institute of
Computing during the 2012-13 term.}

\cventry{2012, 2013}{Basic GNU/Linux Instructor for Freshmen}{GPSL}{University
of Campinas}{Campinas, São Paulo, Brazil}{Basic GNU/Linux classes for Computing
Students}

\section{Languages}
\cvlanguage{Brazilian Portuguese}{Fluent}{Native Language}
\cvlanguage{English}{Fluent}{}

\section{Technical Skills}
\cvitem{Operating Systems}{GNU/Linux (Arch Linux, Debian)}

\cvitem{Programming}{Python, C/C++, Shell Script, Assembly (ARM)}

\cvcomputer{Editors}{vim, gedit}{Version Control}{git}

\cvcomputer{Text Processing}{\LaTeX{}, libreoffice writer}
{Others}{libreoffice calc, libreoffice impress}

\end{document}
