% cv-en for alexandre medeiros
%   by alemedeiros
%
% my curriculum vitae -- english version
%
% created: 2013-05-26
% last revision: 2014-03-01

\documentclass[10pt,a4paper,sans]{moderncv}
\usepackage{fullpage}
\usepackage[british]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{concmath}

% cv style
\moderncvtheme[black]{classic}

% personal info
\firstname{Alexandre}
\familyname{Medeiros}

% optional info
\title{Curriculum Vitae}
\address{202 Eng. Humberto S. de Camargo Street}{13083-780. Campinas, São Paulo,
Brazil}
\mobile{+55~(11)~96624~2947}
\email{alexandre.n.medeiros@gmail.com}
\homepage{http://alemedeiros.sdf.org}
\extrainfo{alemedeiros on gitorious, github}

\begin{document}
\makecvtitle
%\section{Summary}
{
}

\section{Education}
\cventry{2011--}{B.Sc. in Computer Science}{University of Campinas}
{Campinas, São Paulo, Brazil}{}{Ongoing (Expected date of graduation: July 2015).}

\section{Experience}

\subsection{Academic}

\cventry{2013--2014}{Power Estimations for Android based ARM Mobile Devices}{Undergraduate Research}
{University of Campinas}{Campinas, São Paulo, Brazil}
{Advisor: Prof.  Dr. Edson Borin (IC-Unicamp). Co-Advisor: Prof. Dr.  Sandro Rigo (IC-Unicamp).  Funded by a Samsung Scholarship}

\cventry{2012--2014}{Teaching Assistant}{Programa de Apoio Didático}{University of Campinas}{Campinas, São Paulo, Brazil}{
    \begin{itemize}
        \item MC102 -- Algorithm and Computer Programming -- Prof. Hélio Pedrini -- 1st semester of 2014
        \item MC102 -- Algorithm and Computer Programming -- Prof. Cid Carvalho de Souza -- 2nd semester of 2013
        \item MC404 -- Basic Organization of Computers and Assembly Language -- Prof. Edson Borin -- 1st semester of 2013.
        \item MC202 -- Data Structures -- Prof. Tomasz Kowaltowski -- 2nd semester of 2012.
        \item MC202 -- Data Structures -- Prof. Cid Carvalho de Souza -- 1st semester of 2012.
    \end{itemize}
}

\subsection{Volunteer}

\cventry{2011--}{Administrative Officer}{CACo (Centro Acadêmico da Computação)}{University of Campinas}
{Campinas, São Paulo, Brazil}{Unicamp Computing Students' Union (CACo).}

\cventry{2012--2013}{Undergraduate Representative}{Institute of Computing}{University of Campinas}
{Campinas, São Paulo, Brazil}{Undergraduate representative in the Undergraduate Affairs Commission of the Institute of Computing during the 2012-13 term.}

\cventry{2012, 2013}{Basic GNU/Linux Instructor for Freshmen}{GPSL (Grupo Pró Software Livre)}{University of Campinas}
{Campinas, São Paulo, Brazil}{Basic GNU/Linux classes for Computing Students organized by the Pro-Free Software Group (GPSL)}

\section{Technical Skills}
\cvitem{Operating Systems}{GNU/Linux (Arch Linux)}

\cvitem{Programming}{Python, C, Shell Script, Assembly (ARM)}

\cvcomputer{Editors}{vim, gedit}{Version Control}{git}

\cvcomputer{Text Processing}{\LaTeX{}, libreoffice writer} {Others}{libreoffice
calc}

\section{Languages}
\cvlanguage{Brazilian Portuguese}{Fluent}{Native Language}
\cvlanguage{English}{Fluent}{Overall of 8.0 on IELTS Academic test (2013)}

\end{document}
