% cv.tex
%   by alemedeiros <alexandre.n.medeiros _at_ gmail.com>
%
% my curriculum vitae
%
% License:
% % CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% created: 2013-05-26
% last revision: 2024-04-29

\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage{fullpage}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{FiraSans}

\usepackage[super]{nth}

% cv style
\moderncvtheme[purple]{casual}

% personal info
\firstname{Alexandre}
\familyname{Medeiros}

% optional info
% \title{Curriculum Vitae}
\mobile{+55~(11)~96624~2947}
\email{alexandre.n.medeiros@gmail.com}
%\homepage{alemedeiros.dev}
\social[github]{alemedeiros}
\social[linkedin]{alemedeiros}
% \photo[50pt][0.7pt]{alemedeiros}
% \quote{``I must think of something!'' - Alexandre Medeiros}

\renewcommand{\bfdefault}{m}
\renewcommand{\seriesdefault}{l}

\begin{document}

\makecvtitle

\section{Summary}{
  Passionate about technology and computing from an early age, Computer Science
  was always the obvious choice for me. During my studies I fell in love with
  several computing areas, ranging from abstract and high level concepts such as
  Functional Programming, Cryptography, and Theory of Computation to more
  concrete and lower level topics like Distributed Systems, Cloud Computing, and
  Information Security.

  Ever since I started my career, I've developed a great drive to excel, learn,
  and build reliable and scalable systems. Always valuing the importance of the
  collaboration necessary to achieve such results. I'm always looking for
  opportunities to learn and share knowledge with my peers.
}


\section{Experience}

\subsection{\href{https://www.uber.com/}{Uber}}

\cventry{June 2023 --- Present}{Senior Software Engineer}{Session Management Team | Customer Identity Platform}{10 months}{São Paulo (Hybrid)}{
  Implementation for authenticated request metadata injection as a dependency
  for a larger initiative related to PCI DSS compliance Project.\newline
  Definition and implementation for Experiment to determine optimal session
  inactivity TTL.\newline
}

\subsection{\href{https://aiven.io/}{Aiven}}

\cventry{September 2022 --- January 2023}{Senior Software Engineer}{Security Engineering Team}{4 months}{Remote}{
  Automation for integrating user creation and data synchronization for internal
  IT systems as an onboarding project.\newline
  Minor contributions to tasks related PCI DSS.\newline
}

\subsection{\href{https://kirasystems.com/}{Kira Systems} / \href{https://www.litera.com/}{Litera}}

\cventry{January 2022 --- March 2022}{Senior AppSec Developer}{AppSec Team (Litera)}{3 months}{Remote}{
  Gathered and documented the current state of security measures implemented by
  each Litera product, such as SAST, SCA, Penetration Testing etc.\newline
}

\cventry{November 2020 --- January 2022}{Senior Security Developer}{Sectopod (Kira)}{15 months}{Remote}{%
  IDP infrastructure and deployment scripts for multi-product single login.\newline
  Automation of SAST check on build pipeline.\newline
  Maintenance and Vulnerability fixes for the SAML integration.\newline
}

\subsection{\href{https://nubank.com.br}{Nubank}}

\cventry{March 2019 --- August 2020}{Software Engineer}{Security Engineering Squad}{17 months}{São Paulo}{%
  Reimplementation of microservices' loading of Certificate Revocation List.\newline
  Secrets Management System for creating and automatically rotating systems' secrets.\newline
}

\cventry{June 2018 --- March 2019}{Software Engineer Tech Lead}{Rewards Squad}{9 months}{São Paulo}{%
  Led a team from 3 to 4 backend engineers.\newline
  Centralization of custom rules per customer grouping into a single service to deal with desynchronization between multiple shards.\newline
  Cache-powered Backend For Frontend service.\newline
  Design and implementation of extensible and versatile server-client communication format to improve agility for improving on the UI.\newline
}

\cventry{January 2017 --- June 2018}{Software Engineer}{Rewards Squad}{18 months}{São Paulo}{%
  \href{https://www.nubank.com.br/rewards}{Nubank Rewards} Program Launch Plan from Beta phase.\newline
  Program features AB testing and incremental improvements.\newline
}

\cventry{September 2016 --- January 2017}{Software Engineer}{Bills Squad}{4 months}{São Paulo}{%
  Credit Card Bill PDF rendering reimplementation for performance improvement and redesign.\newline
}


\subsection{Google}

\cventry{December 2015 --- March 2016}{Software Engineering Intern}{Health Search}{3 months}{Belo Horizonte}{%
  Exploration project using salient terms.\newline
  Host: Bruno Gusmão.\newline
}

\subsection{Academic}

\cventry{2012 --- 2016}{Teaching Assistant}{\href{https://ic.unicamp.br/}{University of Campinas}}{6 terms}{Campinas}{%
  Data Structures, Algorithm and Computer Programming, Basic Organization of Computers and Assembly Language, and Object Oriented Programming courses.\newline
}

\section{Education}

\cventry{2011 --- 2016}{\href{https://ic.unicamp.br/}{University of Campinas}}{B.Sc. Computer Science}{Campinas}{}{%
  Graduated with honors, as the second in my class. GPA: 8.6 out of 10.\newline
  \href{https://ic.unicamp.br/conheca-o-ic/premiacoes/premiados/}{Pascal Award 2014} (Best academic performance of CS students).\newline
}

\cventry{September 2014 --- August 2015}{\href{https://www.qmul.ac.uk/}{Queen Mary University of London}}{B.Sc. Computer Science}{London}{}{%
  Associate Student (Sponsored by \href{http://www.cienciasemfronteiras.gov.br/}{Science without Borders}).\newline
}

\section{Technical Skills}
\cvitem{Comfortable}{Clojure, Python, Shell Script}
\cvitem{Familiar}{C/C++, Haskell, Go, Java}
\cvitem{Basic}{Lua, JavaScript, Kubernetes}

\section{Languages}
\cvlanguage{Portuguese}{Native Language}{}
\cvlanguage{English}{Fluent}{}
% \cvlanguage{French}{Beginner}{}

\end{document}

% I previously worked at Nubank and actively participated in discussions regarding Clojure and I also took the initiative to teach clojure to several teammates as an onboarding buddy
